LAGOS lake depth

### 2021-08-16 figures/01_geometry.Rmd
show median calculations in fig s5, closes #31

```{r 01_slope_compare, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6.2, fig.height=5.3}
# fig 2B (slope) alternatives
#   gg_slope_base <- nearshore_slope_mean ~ inlake_slope_pnt
#   gg_slope_* <- nearshore_slope* ~ inlake_slope*

inlake_slope_alternatives     <- c("inlake_slope_pnt", "inlake_slope_pnts",
  "inlake_slope_mean",
  "inlake_slope_online_mean",
  "inlake_slopes_online_mean")
nearshore_slope_alternatives  <- c("nearshore_slope_mean",
  "nearshore_slope_online_mean",
  "nearshore_slopes_online_mean")
slope_alternatives   <- setNames(data.frame(expand.grid(
  inlake_slope_alternatives,
  nearshore_slope_alternatives,
  stringsAsFactors = FALSE
)), c("inlake_slope", "nearshore_slope"))

gg_slope_alternative <- function(nearshore_var, inlake_var, dt) {
  # dt <- test
  # nearshore_var <- "nearshore_slope_mean"
  # inlake_var <- "inlake_slope_pnt"
  rsq <- round(broom::glance(
    lm(as.formula(paste0(nearshore_var, " ~ ", inlake_var)), data = dt)
  )$r.squared, 2)
  res <-  ggplot(data = dt) +
    geom_point(aes(.data[[nearshore_var]], .data[[inlake_var]]), size = 1) +
    geom_smooth(aes(.data[[nearshore_var]], .data[[inlake_var]]),
      method = "lm", se = FALSE) +
    # geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    # alpha = 1, fill = "white") +
    annotate("label", x = 0.4, y = 0.52, label = paste0("R^2 == ", rsq),
      parse = TRUE, size = text_size - 0.7) +
    # annotate("label", x = 0.27, y = 0.01,
    #          label = get_formula(
    #            lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)),
    #          size = text_size-0.85, fill = "white", label.size = NA) +
    # geom_abline(slope = 1, intercept = 0) +
    xlab(stringr::str_replace_all(nearshore_var, c("nearshore_" = ""))) +
    ylab(pad_str(stringr::str_replace_all(inlake_var, c("inlake_" = "")),
      18)) +
    xlim(c(0, 0.6)) + ylim(0, 0.6) +
    labs(color = "") +
    theme_opts +
    theme(axis.title = element_text(family = "mono", size = 8))

@@

gg_slope_list[[5]] <- gg_slope_list[[5]] +
  theme(axis.title.x = element_text(face = "bold"))

gg_slope_list[c(1:5)] <- lapply(
  gg_slope_list[c(1:5)], function(x) x +
    theme(
      # axis.title.y = element_blank(),
      axis.title.y = element_text(angle = 0)))

gg_slope_list[c(1:4, 6:9, 11:14)] <- lapply(
  gg_slope_list[c(1:4, 6:9, 11:14)], function(x) x +
    theme(axis.title.x = element_blank(),
      axis.text.x = element_blank()))

gg_slope_list[c(6:15)] <- lapply(
  gg_slope_list[c(6:15)], function(x) x +
    theme(axis.title.y = element_blank(),
      axis.text.y = element_blank()))

xlab <- ggdraw() + draw_label("nearshore")
ylab <- ggdraw() + draw_label("inlake", angle = 90)
cowplot::plot_grid(
  ylab,
  cowplot::plot_grid(
    cowplot::plot_grid(plotlist = gg_slope_list,
      nrow = 5, byrow = FALSE,
      rel_heights = c(rep(0.75, 4), 1),
      rel_widths = c(rep(1, 1),
        rep(0.48, 2))
    ),
    xlab, ncol = 1, rel_heights = c(1, 0.1)),
  ncol = 2, rel_widths = c(0.1, 1))
```

>>>>

```{r 01_slope_compare, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6.4, fig.height=5.3}
# fig 2B (slope) alternatives
#   gg_slope_base <- nearshore_slope_mean ~ inlake_slope_pnt
#   gg_slope_* <- nearshore_slope* ~ inlake_slope*

inlake_slope_alternatives     <- c(
  "inlake_slope_pnt",
  "inlake_slope_pnts",
  "inlake_slope_mean",
  "inlake_slope_online_mean",
  "inlake_slopes_online_mean",
  "inlake_slope_median"
)
nearshore_slope_alternatives  <- c(
  "nearshore_slope_mean",
  "nearshore_slope_online_mean",
  "nearshore_slopes_online_mean",
  "nearshore_slope_median"
)
slope_alternatives   <- setNames(data.frame(expand.grid(
  inlake_slope_alternatives,
  nearshore_slope_alternatives,
  stringsAsFactors = FALSE
)), c("inlake_slope", "nearshore_slope"))

gg_slope_alternative <- function(nearshore_var, inlake_var, dt) {
  # dt <- test
  # nearshore_var <- "nearshore_slope_mean"
  # inlake_var <- "inlake_slope_pnt"
  rsq <- round(broom::glance(
    lm(as.formula(paste0(nearshore_var, " ~ ", inlake_var)), data = dt)
  )$r.squared, 2)
  res <-  ggplot(data = dt) +
    geom_point(aes(.data[[nearshore_var]], .data[[inlake_var]]), size = 1) +
    geom_smooth(aes(.data[[nearshore_var]], .data[[inlake_var]]),
      method = "lm", se = FALSE) +
    # geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    # alpha = 1, fill = "white") +
    annotate("label", x = 0.4, y = 0.52, label = paste0("R^2 == ", rsq),
      parse = TRUE, size = text_size - 0.7) +
    # annotate("label", x = 0.27, y = 0.01,
    #          label = get_formula(
    #            lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)),
    #          size = text_size-0.85, fill = "white", label.size = NA) +
    # geom_abline(slope = 1, intercept = 0) +
    xlab(stringr::str_replace_all(nearshore_var, c("nearshore_" = ""))) +
    ylab(pad_str(stringr::str_replace_all(inlake_var, c("inlake_" = "")),
      18)) +
    xlim(c(0, 0.6)) + ylim(0, 0.6) +
    labs(color = "") +
    theme_opts +
    # theme(axis.title = element_blank()) + ##
    theme(axis.title = element_text(
      family = "mono",
      size = 8))

@@

gg_slope_list[[6]] <- gg_slope_list[[6]] +
  theme(axis.title.x = element_text(face = "bold"))

gg_slope_list[c(1:6)] <- lapply(
  gg_slope_list[c(1:6)], function(x) x +
    theme(
      # axis.title.y = element_blank(),
      axis.title.y = element_text(angle = 0)))

gg_slope_list[c(1:5, 7:11, 13:17, 19:23)] <- lapply(
  gg_slope_list[c(1:5, 7:11, 13:17, 19:23)], function(x) x +
    theme(axis.title.x = element_blank(),
      axis.text.x = element_blank()))

gg_slope_list[c(7:24)] <- lapply(
  gg_slope_list[c(7:24)], function(x) x +
    theme(axis.title.y = element_blank(),
      axis.text.y = element_blank()))

gg_slope_inner <-
  cowplot::plot_grid(plotlist = gg_slope_list,
    nrow = 6, byrow = FALSE,
    rel_heights = c(rep(0.75, 5), 1),
    rel_widths = c(rep(1, 1),
      rep(0.41, 3))
  )

xlab <- ggdraw() + draw_label("nearshore")
ylab <- ggdraw() + draw_label("inlake", angle = 90)
cowplot::plot_grid(
  ylab,
  cowplot::plot_grid(
    gg_slope_inner,
    xlab, ncol = 1, rel_heights = c(1, 0.1)),
  ncol = 2, rel_widths = c(0.1, 1))
```
